Adaptative neigbouring methods applied to telephonic base stations

### 2024-08-14 article.tex
changement d'une variable

For each base station the mean distance to its three nearest neighbours is calculated (we will call this value $\gamma$, in $\unit{km}$), thus making it possible to classify each base station into four different categories listed in Table~\ref{crit_summary}.

@@

\begin{table}[!b]
    \centering
    \caption{Summary of criteria values}
    \label{crit_summary}
    \begin{tabular}{clcc}
        \toprule
        \textbf{$\gamma$} & \textbf{Description} & \textbf{max\_distance} & \textbf{min\_angle} \\
        \cmidrule(lr){1-4}
        $\left[0, 1\right]$ & city center & $\unit[2]{km}$ & $5^\circ$ \\
        $\left]1, 2\right]$ & urban area & $\unit[5]{km}$ & $10^\circ$ \\
        $\left]2, 4\right]$ & extra-urban area & $\unit[10]{km}$ & $15^\circ$ \\
        $\left]4, \infty\right[$ & courntryside & $\unit[15]{km}$ & $20^\circ$ \\
        \bottomrule
    \end{tabular}
\end{table}

>>>>

For each base station the mean distance to its three nearest neighbours is calculated (we will call this value $\gamma_i$, in $\unit{km}$), thus making it possible to classify each base station into four different categories listed in Table~\ref{crit_summary}.

@@

\begin{table}[!b]
    \centering
    \caption{Summary of criteria values}
    \label{crit_summary}
    \begin{tabular}{clcc}
        \toprule
        \textbf{$\gamma_i$} & \textbf{Description} & \textbf{max\_distance} & \textbf{min\_angle} \\
        \cmidrule(lr){1-4}
        $\left[0, 1\right]$ & city center & $\unit[2]{km}$ & $5^\circ$ \\
        $\left]1, 2\right]$ & urban area & $\unit[5]{km}$ & $10^\circ$ \\
        $\left]2, 4\right]$ & extra-urban area & $\unit[10]{km}$ & $15^\circ$ \\
        $\left]4, \infty\right[$ & courntryside & $\unit[15]{km}$ & $20^\circ$ \\
        \bottomrule
    \end{tabular}
\end{table}
